---
title: "R Notebook"
output: html_notebook
---

```{r}
#install.packages(c("tidyverse","quantmod","lubridate","sandwich","lmtest","stargazer"))
#install.packages(c("readr", "dplyr"))
#install.packages("ggplot2")
#install.packages("psych")
#install.packages("corrplot")
#install.packages("estimatr")
#install.packages("stargazer")
#install.packages("modelsummary")
#install.packages("pandoc")
```

```{r}
#suppressWarnings(expr)
options(warn=-1)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
library(readr)
library(tidyverse)
library(quantmod)
library(lubridate)
library(lmtest)
library(sandwich)
library(stargazer)
library(dplyr)
library(ggplot2)
library(psych)
library(corrplot)
library(estimatr)
library(stargazer)
library(pandoc)
library(modelsummary)
```

```{r}
#import silver data
getSymbols("SI=F",
           src = "yahoo",
           from = "2016-01-01",
           to   = "2026-01-01",
           )
silver <- data.frame(
  date = index(`SI=F`),
  silver_price = as.numeric(Ad(`SI=F`))
)
print(head(silver))
print(tail(silver))
```

```{r}
summary(silver)
cat('\n')
str(silver)
```

```{r}
print(colSums(is.na(silver)))
missing_data_silver <- silver[is.na(silver$silver_price), ]
cat("\n")
print(missing_data_silver)
```

```{r}
silver <- na.omit(silver)
cat("Number of NA Value:",colSums(is.na(silver)))
cat('\n')
str(silver)
```

```{r}
ggplot(data = silver, aes(x = date, y = silver_price)) +
  geom_line(color = "steelblue", linewidth = 0.8) + 
  theme_minimal() + 
  labs(
    title = "Silver Futures Price Trend (Continuous Series)",
    subtitle = "Analysis of Silver Prices over Time",
    x = "Date",
    y = "Price (USD)",
    caption = "Source: Yahoo Finance"
  ) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") + 
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12)
  )
```

```{r}
hist(silver$silver_price,
  xlab = "hwy",
  main = "Histogram of hwy",
  breaks = sqrt(length(silver$date))
)
```

```{r}
# compute silver returns
silver <- silver %>%
  mutate(
    silver_return = (silver_price - lag(silver_price))/lag(silver_price)
  )
tail(silver)

```

```{r}
cat("Number of NA Value:",colSums(is.na(silver)),"\n")
silver <- na.omit(silver)
cat("Number of NA Value:",colSums(is.na(silver)),"\n")
str(silver)
```

```{r}
ggplot(data = silver, aes(x = date, y = silver_return)) +
  geom_line(color = "steelblue", linewidth = 0.8) +  
  theme_minimal() + 
  labs(
    title = "Silver Futures Return (Continuous Series)",
    subtitle = "Analysis of Silver Return Value over Time",
    x = "Date",
    y = "Return",
    caption = "Source: Yahoo Finance"
  ) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") + 
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12)
  )
```

```{r}
hist(silver$silver_return,
  xlab = "hwy",
  main = "Histogram of hwy", breaks = sqrt(length(silver$date))
)
```
```{r}
describe(silver)
```
```{r}
summary(silver)
```

```{r}
#import Gold data
getSymbols("GC=F",
           src = "yahoo",
           from = "2016-01-01",
           to   = "2026-01-01")
gold <- data.frame(
  date = index(`GC=F`),
  gold_price = as.numeric(Ad(`GC=F`))
)
print(head(gold))
print(tail(gold))

```

```{r}
summary(gold)
cat('\n')
str(gold)
```

```{r}
print(colSums(is.na(gold)))
missing_data_gold <- gold[is.na(gold$gold_price), ]
cat("\n")
print(missing_data_gold)
```

```{r}
gold <- na.omit(gold)
cat("Number of NA Value:",colSums(is.na(gold)))
cat('\n')
str(gold)
```

```{r}
ggplot(data = gold, aes(x = date, y = gold_price)) +
  geom_line(color = "steelblue", linewidth = 0.8) + 
  theme_minimal() + 
  labs(
    title = "Gold Futures Price Trend (Continuous Series)",
    subtitle = "Analysis of Gold Prices over Time",
    x = "Date", y = "Price (USD)",
    caption = "Source: Yahoo Finance"
  ) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") + 
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12)
  )
```

```{r}
hist(gold$gold_price,
  xlab = "hwy",
  main = "Histogram of gold+",
  breaks = sqrt(length(gold$date))
)
```

```{r}
# compute Gold returns
gold <- gold %>%
  mutate(
    gold_return = (gold_price - lag(gold_price))/lag(gold_price)
  )
tail(gold)
```

```{r}
cat("Number of NA Value:",colSums(is.na(gold)),"\n")
gold <- na.omit(gold)
cat("Number of NA Value:",colSums(is.na(gold)),"\n")
str(gold)
```

```{r}
ggplot(data = gold, aes(x = date, y = gold_return)) +
  geom_line(color = "steelblue", linewidth = 0.8) + 
  theme_minimal() + 
  labs(
    title = "Gold Futures Return (Continuous Series)",
    subtitle = "Analysis of Gold Return Value over Time",
    x = "Date",
    y = "Return",
    caption = "Source: Yahoo Finance"
  ) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12)
  )
```
```{r}
describe(gold)
```


```{r}
hist(gold$gold_return,
  xlab = "hwy",
  main = "Histogram of hwy",
  breaks = sqrt(length(gold$date))
)
```

```{r}
summary(gold)
```


```{r}
# import cds data 
cds <- read.csv("us_cds.csv")
cds$Date <- as.Date(cds$Date, format = "%m/%d/%Y")
cds <- cds %>% rename(date = Date)
```

```{r}
cds <- cds %>%
  arrange(date) %>%
  mutate(
    cds_change = (Price - lag(Price))/lag(Price)
  )
```

```{r}
cds <- cds %>%
  rename(cds_price = Price) %>%
  select(date, cds_price, cds_change)
cds
```

```{r}
head(cds)
```

```{r}
tail(cds)
```

```{r}
summary(cds)
```

```{r}
describe(cds)
```


```{r}
str(cds)
```

```{r}
print(colSums(is.na(cds)))
missing_data_cds <- cds[is.na(cds$cds_change), ]
cat("\n")
print(missing_data_cds)
```

```{r}
cds <- na.omit(cds)
cat("Number of NA Value:",colSums(is.na(cds)))
cat('\n')
str(cds)
```

```{r}
cds[which.min(cds$cds_change), ]
```

```{r}
ggplot(data = cds, aes(x = date, y = cds_change)) +
  geom_line(color = "steelblue", linewidth = 0.8) + 
  theme_minimal() +
  labs(
    title = "CDS Change Trend",
    subtitle = "Analysis of CDS Change over Time",
    x = "Date",
    y = "Change (USD)",
    caption = "Source: investing.com"
  ) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") + 
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12)
  )
```

```{r}
hist(cds$cds_change,
  xlab = "hwy", main = "Histogram of hwy", breaks = 50
)
```

```{r}
#import VIX
getSymbols("VIXCLS", src = "FRED", from = "2016-01-01", to = "2026-01-01")
vix <- data.frame(
  date = index(VIXCLS),
  vix = as.numeric(VIXCLS$VIXCLS)
)
print(head(vix))
print(tail(vix))
summary(vix)
cat('\n')
str(vix)
```

```{r}
print(colSums(is.na(vix)))
missing_data_vix <- vix[is.na(vix$vix), ]
cat("\n")
print(missing_data_vix)
```

```{r}
vix <- na.omit(vix)
cat("Number of NA Value:",colSums(is.na(vix)))
cat('\n')
str(vix)
```

```{r}
# import us dollar
getSymbols("DTWEXBGS", src = "FRED", from = "2016-01-01", to = "2026-01-01")
usd <- data.frame(
  date = index(DTWEXBGS),
  usd_price = as.numeric(DTWEXBGS$DTWEXBGS)
)
print(head(usd))
print(tail(usd))
summary(usd)
cat('\n')
str(usd)
```

```{r}
print(colSums(is.na(usd)))
missing_data_usd <- usd[is.na(usd$usd_price), ]
cat("\n")
print(missing_data_usd)
```

```{r}
usd <- na.omit(usd)
cat("Number of NA Value:",colSums(is.na(usd)))
cat('\n')
str(usd)
```

```{r}
# compute usd  returns
usd <- usd %>%
  mutate(
    usd_return = (usd_price - lag(usd_price))/lag(usd_price)
  ) %>%
  na.omit()
```

```{r}
# merge data 
data <- silver %>%
  inner_join(gold, by="date") %>%
  inner_join(cds, by="date") %>%
  inner_join(vix, by="date") %>%
  inner_join(usd, by="date") %>%
  arrange(date) %>%
  drop_na()

```

```{r}
data
```

```{r}
summary(data)
```

```{r}
str(data)
```

```{r}
desc <- describe(data)

desc_table <- as.data.frame(desc)
desc_table <- round(desc_table, 6)
desc_table <- desc_table[, c("mean", "sd", "min", "max", "skew", "kurtosis")]

desc_table


```

```{r}
corrdata <- data[, c("silver_return","cds_change","vix","usd_return")]
corrdata

M <- cor(corrdata, use = "complete.obs")

corrplot(M, method = "color", 
         type = "upper", 
         addCoef.col = "black", 
         tl.col = "black", tl.srt = 45) 
```
```{r}
corrdata <- data[, c("gold_return","cds_change","vix","usd_return")]
corrdata

M <- cor(corrdata, use = "complete.obs")

corrplot(M, method = "color", 
         type = "upper", 
         addCoef.col = "black", 
         tl.col = "black", tl.srt = 45) 

```

```{r}
#OLS Silver Simple Model
model<- lm(silver_return~cds_change, data = data)
summary(model)
```

```{r}
#Robust Silver Simple Model
model1 <- lm_robust(silver_return~cds_change, data = data)
summary(model1)
```

```{r}
# Robust Silver Multiple Model
model2 <- lm_robust(silver_return~ cds_change + vix+ usd_return, data = data)
summary(model2)
```

```{r}
# install.packages("modelsummary")
#install.packages("pandoc")
#library(pandoc)



# Create the table
modelsummary(list("Simple" = model1, "Multiple" = model2), 
             stars = TRUE, 
             title = "Robust Regression Results For Silver",output = "Silver_table.docx")
```

```{r}
#OLS Gold Simple Model
model_gold<- lm(gold_return~cds_change, data = data)
summary(model_gold)
```

```{r}
#Robust Gold Simple Model
model1_gold <- lm_robust(gold_return~cds_change, data = data)
summary(model1_gold)
```

```{r}
# Robust Gold Multiple Model
model2_gold <- lm_robust(gold_return~ cds_change + vix+ usd_return, data = data)
summary(model2)
```

```{r}
modelsummary(list("Simple" = model1_gold, "Multiple" = model2_gold), 
             stars = TRUE, 
             title = "Robust Regression Results Of Gold",output = "Gold_table.docx")

```

```{r}
#silver and cds plot
ggplot(data, aes(x = cds_change, y = silver_return)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(
    title = "Relationship between Silver Returns and CDS Changes",
    x = "CDS Change",
    y = "Silver Return"
  ) +
  theme_minimal()
#gold and cds plot
ggplot(data, aes(x = cds_change, y = gold_return)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(
    title = "Relationship between gold Returns and CDS Changes",
    x = "CDS Change",
    y = "gold Return"
  ) +
  theme_minimal()
```

```{r}
#robustness tests silver
#lagged cds 
data$cds_change_lag <- lag(data$cds_change)
model1_silver_lag <- lm_robust(silver_return ~ cds_change_lag, data=data)
summary(model1_silver_lag)
model2_silver_lag <- lm_robust(silver_return ~ cds_change_lag + vix + usd_return, data=data)
```


```{r}
modelsummary(list("Simple" = model1_silver_lag, "Multiple" = model2_silver_lag), 
             stars = TRUE, 
             title = "Robust Regression Results Of silver(with lagged cds)",output = "silver_lag_table.docx")
```

```{r}
#robustness tests gold
#lagged cds 
data$cds_change_lag <- lag(data$cds_change)
model1_gold_lag <- lm_robust(gold_return ~ cds_change_lag, data=data)
summary(model1_gold_lag)
model2_gold_lag <- lm_robust(gold_return ~ cds_change_lag + vix + usd_return, data=data)

```
```{r}
modelsummary(list("Simple" = model1_gold_lag, "Multiple" = model2_gold_lag), 
             stars = TRUE, 
             title = "Robust Regression Results Of Gold(with lagged cds)",output = "gold_lag_table.docx")

```


```{r}
#considering covid
data$covid <- ifelse(
  data$date >= as.Date("2020-03-01") &
  data$date <= as.Date("2021-12-31"),1,0)

model1_silver_covid <- lm_robust(
  silver_return ~cds_change+ covid + cds_change:covid,
  data = data
)
summary(model1_silver_covid)

model2_silver_covid <- lm_robust(
  silver_return ~ cds_change + vix + usd_return +
  covid + cds_change:covid,
  data = data
)

summary(model2_silver_covid)
```


```{r}
modelsummary(list("Simple" = model1_silver_covid, "Multiple" = model2_silver_covid), 
             stars = TRUE, 
             title = "Robust Regression Results Of silver(covid)",output = "silver_covid_table.docx")
```


